\texttt{SuperScreen}: An open-source package for simulating the magnetic response of two-dimensional superconducting devices

### 2021-11-20 main.tex

\section{Numerical considerations}
\label{appendix:numerics}
While the numerical method described in Section~\ref{section:implementation} is generally quite robust, it can break down for certain extreme geometries. The stream function $g(x, y)$ represents the local magnetization or density of infinitesimal current loops. The $z$-component of the magnetic field at position $\vec{r}=(x, y, z)$ from a film $F$ with stream function $g$ lying in a plane parallel to the $x-y$ plane at vertical position $z'$ is given by (see Equations~\ref{eq:field_from_kernel} and \ref{eq:kernels}):
\begin{align}
\label{eq:hz-from-kernel}
\begin{split}
    H_z(\vec{r}) &= \int_F Q_z(\vec{r},\vec{r}')g(x', y')\,\mathrm{d}^2r',\,\text{where}\\
    Q_z(\vec{r}, \vec{r}') &=  \frac{2(z-z')^2-\rho^2}
            {4\pi[(z-z')^2+\rho^2]^{5/2}}
\end{split}
\end{align}
and $\rho=\sqrt{(x-x')^2+(y-y')^2}$. Eq.~\ref{eq:hz-from-kernel} is exact for a continuous stream function $g$. However, the discretized version of Eq.~\ref{eq:hz-from-kernel}, in which the double integral over the film area $F$ is replaced by a sum over triangular mesh elements, is only valid if $z-z'$, the vertical distance between the film and the point at which the field is being evaluated, is larger than the typical distance $\delta r$ between vertices in the mesh representing the film. For $z-z'\lesssim\delta r$, the field $H_z(\vec{r})$ resembles that of a set of isolated dipoles located at the mesh vertex positions, rather than that of a continuous sheet of current. This can lead to unphysical results when evaluating the field very close to the surface of a film (for example using \inline{Solution.field_at_position()}), or when solving models involving multi-layer structures where the vertical spacing between layers is much smaller than the lateral extent of the films, in which case the iterative calculation (Section~\ref{section:model:multilayer}) may not converge.

@@

The limitation described above can be seen in the model of the largest SQUID susceptometer described in Section~\ref{section:examples:scanning-squid}, which has a field coil outer radius of $8\,\um$ and a total modeled area of roughly $600\,\um^2$.

>>>>

\section{Numerical considerations}
\label{appendix:numerics}
While the numerical method described in Section~\ref{section:implementation} is generally quite robust, it can break down for certain extreme geometries. The stream function $g(x, y)$ represents the local magnetization or density of infinitesimal current loops. The $z$-component of the magnetic field at position $\vec{r}=(x, y, z)$ from a film $F$ with stream function $g$ lying in a plane parallel to the $x-y$ plane at vertical position $z'$ is given by (see Equations~\ref{eq:field_from_kernel} and \ref{eq:kernels}):
\begin{align}
\label{eq:hz-from-kernel}
\begin{split}
    H_z(\vec{r}) &= \int_F Q_z(\vec{r},\vec{r}')g(x', y')\,\mathrm{d}^2r',\,\text{where}\\
    Q_z(\vec{r}, \vec{r}') &=  \frac{2(z-z')^2-\rho^2}
            {4\pi[(z-z')^2+\rho^2]^{5/2}}
\end{split}
\end{align}
and $\rho=\sqrt{(x-x')^2+(y-y')^2}$. Eq.~\ref{eq:hz-from-kernel} is exact for a continuous stream function $g$. However, the discretized version of Eq.~\ref{eq:hz-from-kernel}, in which the double integral over the film area $F$ is replaced by a sum over triangular mesh elements, is only valid if $z-z'$, the vertical distance between the film and the point at which the field is being evaluated, is larger than the typical distance $\delta r$ between vertices in the mesh representing the film. For $z-z'\lesssim\delta r$, the field $H_z(\vec{r})$ resembles that of a discrete set of isolated dipoles located at the mesh vertex positions, rather than that of a continuous sheet of current. This can lead to unphysical results when evaluating the field very close to the surface of a film (for example using \inline{Solution.field_at_position()}), or when solving models involving multi-layer structures where the vertical spacing between layers is much smaller than the lateral extent of the films, in which case the iterative calculation (Section~\ref{section:model:multilayer}) may not converge.

The limitation described above can be seen in the model of the largest SQUID susceptometer described in Section~\ref{section:examples:scanning-squid}, which has a field coil outer radius of $8\,\um$ and a total modeled area of roughly $600\,\um^2$. As shown in Figure~\ref{fig:xlarge-dz-dr}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{examples/images/xlarge-dz-dr.png}
    \caption{\SuperScreen results may be unreliable for multi-layer models where the spacing between layers is smaller than the typical vertex-to-vertex distance, $\delta r$. (a) Field coil - pickup loop mutual inductance for the largest SQUID suscepometer modeled in Section~\ref{section:examples:scanning-squid} as a function of the minimum vertical spacing between layers, $\delta z$. The simulated mutual inductance is shown with blue circles, and a histogram of the mesh vertex-to-vertex distances $\delta r$ is shown in orange (arb. $y$ axis units). When $\delta z\lesssim\delta r$, the model significantly underestimates the mutual inductance. (b) and (c): Out-of-plane magnetic field $\mu_0H_z$ evaluated at the plane of the pickup loop (W1 layer) for (b) the nominal layer spacing with $\delta z<\delta 2$ (indicated with a black $\times$ in (a)) and (c) $\delta z > \delta r$ (indicated with a black $+$ in (a)).}
    \label{fig:xlarge-dz-dr}
\end{figure}

@@
